AFQ-Insight

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

To relate the diffusion in each voxel to the macro-structure of
long-range connections between different brain regions, methods for
computational tract-tracing from diffusion MRI, or tractography, combine
the estimates of fiber orientations in each voxel to form streamlines
that traverse the volume of the white matter \cite{Conturo1999-je,
Mori2002-qi}. These methods have been under increased scrutiny and
several lines of investigation have raised critiques of their validity
\cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
have been efforts to shore up the inferences made with these methods
\cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
tracts requires extraordinary evidence, and delineating
the exact cortical termination of the streamlines in the gray matter
is still prone to error, there is little dispute that tractography
can accurately define the location of several major white matter
tracts that are known to exist within the core of the white matter
\cite{Maier-Hein2017-vb}.

@@

In some previous tractometry-based studies, tissue properties along
the length of each tract were summarized by taking the mean along
each bundle, but there is a large body of evidence showing that there
is systematic variability along the trajectory of each bundle. This
justifies retaining the individual samples along the length of each
bundle \cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this
retains important information about each individual's white matter, it
also presents statistical challenges due to the dimensionality of the
data. Based on tractometry, researchers may choose to compare different
individuals to each other. This is usually done according to one of the
following approaches:

>>>>

To relate the diffusion in each voxel to the macro-structure of
long-range connections between different brain regions, methods for
computational tract-tracing from diffusion MRI, or tractography, combine
the estimates of fiber orientations in each voxel to form streamlines
that traverse the volume of the white matter \cite{Conturo1999-je,
Mori2002-qi}. These methods have been under increased scrutiny and
several lines of investigation have raised critiques of their validity
\cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
have been efforts to shore up the inferences made with these methods
\cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
tracts requires extraordinary evidence, and delineating
the exact cortical termination of the streamlines in the gray matter
is still prone to error, there is little dispute that tractography
can accurately define the location of several major white matter
tracts that are known to exist within the core of the white matter
\cite{Maier-Hein2017-vb, Catani2002-vu}.

@@

In some previous tractometry-based studies, tissue properties along
the length of each tract were summarized by taking the mean along
each bundle, but there is a large body of evidence showing that there
is systematic variability in the values of diffusion metrics along the trajectory of each bundle. This
justifies retaining the individual samples along the length of each
bundle \cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this
retains important information about each individual's white matter, it
also presents statistical challenges due to the dimensionality of the
data. Based on tractometry, researchers may choose to compare different
individuals to each other. This is usually done according to one of the
following approaches:
